---
output:
  html_document:
    theme: null
    highlight: null
    css: styles.css
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)

## Global options
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
```

```{r load_packages}
library(tidyverse)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(rgdal)
```

```{r load_bounds, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
source("prep hunger index.r")

# 
pal = colorFactor("YlGnBu", msoa_bounds@data$RiskRateQ)
```

<!--html_preserve-->
<!-- Google Tag Manager (noscript) -->
<noscript><iframe src="https://www.googletagmanager.com/ns.html?id=GTM-KKTZ7CB"
height="0" width="0" style="display:none;visibility:hidden"></iframe></noscript>
<!-- End Google Tag Manager (noscript) -->

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;border:none;}
.tg td{padding:1px 5px;border-style:solid;border-width:0px;overflow:hidden;word-break:normal;}
.tg .tg-us36{border-color:inherit;vertical-align:top}
</style>

<div style="z-index: 1; position: absolute; top: 0px; left: 50px; background-color: rgba(255, 255, 255, 0.6); padding: 5px 5px 5px 5px; font-size: 12px">
  <h3>Risk of food insecurity in England</h3>
  <p>This map shows population-level risk of household food insecurity in English neighbourhoods.</p>
  <p>Data are from <a href="https://www.sciencedirect.com/science/article/abs/pii/S0143622817301340" target="_blank">Smith et al. (2018) Identifying populations and areas at greatest risk of household food insecurity in England</a></p>
</div>
<!--/html_preserve-->

```{r map}
leaflet(msoa_bounds,
        width = "100%", height = "100%", padding = 0,
        options = leafletOptions(minZoom = 5, maxZoom = 12, attributionControl = T)) %>% 
  
  # centre map on Whitendale Hanging Stones, the centre of GB: https://en.wikipedia.org/wiki/Centre_points_of_the_United_Kingdom
  setView(lat = 54.00366, lng = -2.547855, zoom = 7) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  
  # LRF
  addPolygons(weight = 1, smoothFactor = 0.5, fillOpacity = 0.7,
              color = "#5C747A", fillColor = ~pal(RiskRateQ),
              highlightOptions = highlightOptions(color = "#9CAAAE", weight = 2, bringToFront = T),

              label = ~msoa11nm,

              popup = ~paste(
                "<b>", msoa11nm, "</b><br/><br/>",
                "Risk quintile: ", RiskRateQ
              ),
              group = "MSOA") %>%

  addSearchFeatures(
    targetGroups  = "MSOA",
    options = searchFeaturesOptions(zoom=10, openPopup=TRUE)
  ) %>%
  
  addLegend("bottomright", pal = pal, 
            values = ~RiskRateQ,
            title = "Food insecurity risk\n(5 is highest risk)",
            opacity = 1
  )
```
